### 2014-11-13 tex/results.tex
tigthening results

\section{Evaluation}
\label{sec:eval}
In this section we evaluate the effectiveness of the \symtxt{}
approach at analyzing programs with unbounded complex data input in
the context of symbolic execution. In order to perform our evaluation
we implement the \symtxt{} technique and evaluate its efficiacy on
three Java data structure artifacts. We compare the results of the
\symtxt{} approach with other state of the art techniques that
initialize complex data input symbolically. We first describe the tool
infrastructure we use to implement our approach.

\subsection{Tool Support}
We implement the \symtxt{} as an extension to the symbolic execution
engine of Java PathFinder(JPF)---Symbolic Pathfinder
(SPF)~\cite{visser:ase03,Pasareanu:ISSTA08,pasareanu:ase10,DBLP:journals/ase/PasareanuVBGMR13}. SPF
is an open source engine for performing symbolic execution on Java
bytecode. SPF overwrites the concrete execution semantics of Java
bytecode to generate a symbolic execution tree. SPF contains an
implementation for GSE with lazy initialization. Recent work also
provides implementations of the lazier and lazier\# algorithms in the
SPF framework~\cite{Hillery:2014}.

@@

We create a new extension to SPF in order to implement the~\symtxt{}
approach. In addition to the operations presented in the Javalite
semantics, the implementation contains support for operations over
integers. Examples of bytecode that we overwrite in the SPF engine are
as follows: (i) field access bytecodes, e.g., GETFIELD and ALOAD
bytecodes, to implement the field-access and summarize rules
in~\figref{fig:symInit} and~\figref{fig:fHeap}(a), (ii) the field
write bytecodes, e.g., PUTFIELD and ASTORE bytecodes, to implement the
field-write rules in~\figref{fig:fHeap}(a), (iii) checking equality of
references bytecode, IF\_ACMPEQ and IF\_ACMPNE, to implement the
equals references-true and references-false rules in~\figref{fig:eqs}
(iv) linear arithmetic operations on integers and (v) comparison
operations on integers. We are currently working on adding support for
floating point operations, arrays, and bit-operations.

The default constraints library in SPF requires constraints to be in
the CNF form, and is unable to support constraints generated by the
\symtxt{} approach since they contain disjunctions. Transforming the
constraints generated by the \symtxt{} approach into a CNF form proved
to be inefficient. We use the \texttt{jConstraints} library that
provides support to handle arbitrary
constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses the z3
solver,~\cite{z3}, as the backend to solve the constraints. We
leverage the incremental solving feature in z3 in our experiments. We
also implement other optimizations that cache and re-use solutions to
previous constraints. These optimizations are an important part of our
implementation because only small portions of the heap constraint
changes from one state to another.

@@

The goal of our technique to evaluate the efficiacy of our approach
with respect to other state of the art algorithms for symbolic
execution for dealing for unbounded complex data input. We empirically
evaluate \symtxt{} by considering the following research questions:

@@

\item {\bf RQ2:} Does \symtxt{} technique enable other back-end
  approaches that can leverage its output?
\end{description}

@@

To perform our study we compile all our artifacts and run the analysis
on \nsr{the machine.. sthuff about the time bound etc.}.

>>>>

\section{Evaluation}
\label{sec:eval}
In this section we evaluate the effectiveness of the \symtxt{}
approach at analyzing programs with unbounded complex data input in
the context of symbolic execution. In order to perform our evaluation
we implement the \symtxt{} technique and evaluate its efficiacy on
three Java data structure artifacts. We compare the results of the
\symtxt{} approach with other state of the art techniques that
initialize complex data input symbolically.

Symbolic Pathfinder
(SPF)~\cite{visser:ase03,Pasareanu:ISSTA08,pasareanu:ase10,DBLP:journals/ase/PasareanuVBGMR13}. SPF
is an open source engine for performing symbolic execution on Java
bytecode. SPF overwrites the concrete execution semantics of Java
bytecode to generate a symbolic execution tree. SPF contains an
implementation for GSE with lazy initialization. Recent work also
provides implementations of the lazier and lazier\# algorithms in the
SPF framework~\cite{Hillery:2014}.

@@

We create a new extension to SPF in order to implement the~\symtxt{}
approach. In addition to the operations presented in the Javalite
semantics, the implementation contains support for operations over
integers. Examples of bytecode that we overwrite in the SPF engine are
as follows: (i) field access bytecodes, e.g., GETFIELD and ALOAD
bytecodes, to implement the field-access and summarize rules
in~\figref{fig:symInit} and~\figref{fig:fHeap}(a), (ii) the field
write bytecodes, e.g., PUTFIELD and ASTORE bytecodes, to implement the
field-write rules in~\figref{fig:fHeap}(a), (iii) checking equality of
references bytecode, IF\_ACMPEQ and IF\_ACMPNE, to implement the
equals references-true and references-false rules in~\figref{fig:eqs}
(iv) linear arithmetic operations on integers, and (v) comparison
operations on integers. We are currently working on adding support for
floating point operations, arrays, and bit-operations.  We use the
\texttt{jConstraints} library that provides support to handle the heap
constraints~\cite{ase2014-ghilrr,jpf2014-dghirr}. It uses the z3
solver,~\cite{z3}, as the backend to solve the constraints. We
leverage the incremental solving feature in z3 in our experiments. We
also implement other optimizations that cache and re-use solutions to
previous constraints. These optimizations are an important part of our
implementation because only small portions of the heap constraint
changes from one state to another.

%The default constraints library in SPF requires constraints to be in
%the CNF form, and is unable to support constraints generated by the
%\symtxt{} approach since they contain disjunctions. Transforming the
%constraints generated by the \symtxt{} approach into a CNF form
%proved to be inefficient.

@@

The goal of our technique to evaluate the efficiacy of our approach
with respect to other state of the art algorithms for symbolic
execution for dealing for unbounded complex data input. We empirically
evaluate \symtxt{} by considering the following research question:

@@

%\item {\bf RQ2:} Does \symtxt{} technique enable other back-end
%  approaches that can leverage its output?
\end{description}

@@
